\section{Introduction}
\paragraph{}
\ac{sl}s play a crucial role in facilitating communication for individuals with hearing impairments. However, comprehending and interpreting \ac{sl} poses challenges for those who are not familiar with its intricacies. To address this, there is a growing demand for technology-based solutions that can enable \ac{slr} and enhance communication between signers and non-signers.
\paragraph{}
The primary objective of this chapter is to introduce the conception of TAKALEM Gloves, a wearable technology-based system for \ac{slr}. These gloves are designed to capture hand gestures and translate them into corresponding signs or text in real-time, enabling seamless communication between individuals who use \ac{sl} and those who do not.
\paragraph{}
This chapter focuses on the hardware architecture and configuration of the TAKALEM Gloves. It explores the technological aspects of the gloves, including the selection of microcontrollers, sensors, and other essential components. Understanding the underlying hardware is crucial for gaining insights into the system's capabilities and limitations.
\paragraph{}
Furthermore, the motivation behind the development of TAKALEM Gloves is explored in this chapter. The ability to bridge the communication gap between signers and non-signers holds significant implications in various domains. In the field of education, the gloves can be utilized to teach \ac{sl} to non-signers, fostering inclusivity and promoting accessibility in educational settings. Within the healthcare sector, the gloves facilitate effective communication between healthcare providers and patients with hearing impairments, enhancing the quality of care and patient experience.
\paragraph{}
Moreover, the integration of TAKALEM Gloves into smart homes and devices offers opportunities for seamless interaction and control. Users can communicate with their smart devices using \ac{sl}, enhancing convenience and accessibility in the context of home automation. Additionally, the gloves prove invaluable in emergency situations where communication is critical, facilitating swift and efficient communication between individuals in high-stress scenarios.
\paragraph{}
This chapter sets the stage for the subsequent sections, which will delve into specific aspects of the \ac{slr} system. By understanding the significance of \ac{sl}s, the diverse applications of TAKALEM Gloves, and the underlying motivation, we can recognize the importance of developing an accurate and reliable system that empowers individuals with hearing impairments.