\section{Deep Learning for \ac{slr}}
\paragraph{}
\ac{dl}, a subfield of \ac{ml}, has revolutionized various domains by enabling the automatic learning of intricate patterns and representations from raw data. In \ac{slr}, \ac{dl} proves to be a promising approach due to its ability to process and analyze complex visual and temporal information.
\paragraph{}
\ac{nn} serve as the foundation of \ac{dl} models. These computational structures are inspired by the biological neurons in the human brain and consist of interconnected layers of artificial neurons. \ac{cnn} are widely employed in image recognition tasks, including the analysis of hand gestures in \ac{sl}. \ac{cnn}s leverage convolutional layers to automatically learn spatial features from input images, enabling the model to discern intricate patterns and variations.
\paragraph{}
In addition to \ac{cnn}s, \ac{rnn} play a vital role in \ac{slr}. \ac{rnn}s are particularly effective in handling sequential data, which is inherent in \ac{sl} gestures. \ac{rnn}s can capture the temporal dependencies in a sequence of gestures and retain information over time. \ac{lstm} networks, a type of \ac{rnn}, excel in modeling long-range dependencies and have demonstrated promising results in \ac{slr} tasks.
\paragraph{}
Training and optimization are essential steps in the \ac{dl} workflow. During the training phase, a \ac{nn} is exposed to labeled training data, and its internal parameters are adjusted to minimize the discrepancy between predicted and actual outputs. Backpropagation, a gradient-based optimization algorithm, is commonly used to update the model's parameters. The training process is iterative, and the model undergoes multiple epochs to improve its performance gradually.
\paragraph{}
Despite the remarkable potential of \ac{dl} in \ac{slr}, it comes with its own set of challenges and limitations. One major challenge is the scarcity of annotated \ac{sl} datasets, which hinders the training process and necessitates domain-specific data collection efforts. Overfitting, a phenomenon where the model performs well on training data but fails to generalize to unseen data, is another challenge that requires careful regularization techniques.
\paragraph{}
Moreover, \ac{dl} models often demand significant computational resources, including high-performance computing units and memory capacity. The interpretability of \ac{dl} models is another concern, as they are often seen as "black boxes" that make it challenging to understand the internal decision-making process.
\paragraph{}
In conclusion, \ac{dl} techniques offer immense potential for \ac{slr}, enabling the automatic extraction of meaningful representations from visual and temporal data. This section has provided a comprehensive overview of the key concepts, methodologies, and challenges associated with \ac{dl} in the context of \ac{slr}. By leveraging \ac{dl}, we can unlock new possibilities for accurate and real-time interpretation of \ac{sl} gestures.