\section{Requirements specification}
In order to design and implement an effective sign language recognition system, it is important to first identify and analyze the specific requirements of the system. These requirements include both functional and non-functional requirements, and are critical in guiding the development process. The following subsections detail the specific requirements of the Takalem gloves project.

\subsection{Functional Requirements}
The functional requirements for the Takalem gloves project include the following:

\begin{enumerate}
	\item[Collecting sensor data] The gloves should be able to collect sensor data from the hand movements of the user.
	\item[Preprocessing the data] The collected data should be preprocessed and prepared for further analysis and training.
	\item[Developing a deep learning model] A deep learning model should be designed and implemented to recognize sign language gestures from the collected and preprocessed data.
	\item[Testing and evaluating the model] The developed model should be tested and evaluated on a variety of performance metrics to ensure its accuracy and effectiveness.
\end{enumerate}
\subsection{Non-functional Requirements}
In addition to the functional requirements, the Takalem gloves project also has several non-functional requirements. These requirements include:

\begin{enumerate}
	\item[Low latency] The gloves should have low latency in order to provide real-time feedback to the user.
	\item[Low power consumption] The gloves should consume low power in order to be energy-efficient and extend battery life.
	\item[High accuracy] The developed model should have high accuracy in recognizing sign language gestures in order to be useful in practical applications.
	\item[User-friendliness] The gloves should be easy to use and operate for the user, with intuitive gestures and clear feedback.
\end{enumerate}
Overall, these requirements will guide the design and implementation of the Takalem gloves project, ensuring that it is effective, efficient, and user-friendly.